---
title: "First Pass"
author: "Jason Neumeyer"
date: "January 25, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the first pass I took at putting together some of the analyses which we talked about last week. The first step I took was to create a new variable called tv_prefer which was just the difference between the respondents MSNBC preference and FOX preference.  In doing so, this allowed me to determine whether the preferred MSNBC (number > 0) or FOX (number < 0) rather quickly.

After this, I subset the data to include those who preferred MSNBC or FOX and were in the control, choice, and assigned conditions. This created the seperate subgroups from which our comparisons could be drawn.  To determine the levels of immigration support each group had, I took the mean of our three immigration questions (immig_increased, taxes_pos, jobs_pos) and scaled them from 0 to 1 with higher numbers indicating higher support for immigration based on these 3 questions. 

NEW STUFF!

I added in the neither category to the three groups (control, assigned, choice) and calcuated the mean and CIs. Additionally, there are now two ggplot graphs below which show the control vs free choice and control vs assigned - I did not spend too much time on the formatting, so that can always be cleaned up. I did seperate each group into its own x coordinate because when the 3 difference preferences were shown toegether, they were very difficult to read. Maybe there is another way to seperate them that we could discuss?

Talk to you all soon!

NEW NEW STUFF!

I was able to seperate the three panels by preference in our graphs below - I also noticed that I had made a mistake in the CIs when I initially sent this last week. That error has been fixed, so these basic descriptive graphs should be good to go!

## load packages - 

```{r, warning=FALSE, message=FALSE}
library(here)
library(readr)
library(tidyverse)
library(ggplot2)
library(expss)
library(broom)
library(purrr)
```

## set wd and load data - 

```{r}
setwd("C:/Users/Owner/Desktop/UW-Milwaukee Graduate Year 2/Lab Meeting/Data")

dat <- read.csv("immigration_20191219_clean.csv")

## View(dat)
```

# preference variable -  

```{r}
tv_prefer <- dat$tv_msnbc - dat$tv_fox
dat["tv_prefer"] <- tv_prefer

## View(dat)
```

# H3 - effects of corrective information condition on preferred media choice 

Here, I subset the data to include those individuals who were part of the control group and preferred either FOX or MSNBC and calculated their mean immigration levels based on the 3 immigration questions asked after they would have read the story (if they were not in control). I also calculated their CIs in the table belo.

Added those in the neither category!

# control - 

```{r}
preferMSNBC_Control <- subset(dat, tv_prefer > 0 & condition == "control")
## View(preferMSNBC_Control)

preferFOX_Control <- subset(dat, tv_prefer < 0 & condition == "control")
## View(preferFOX_Control)

preferneither_control <- subset(dat, tv_prefer == 0 & condition == "control")
## View(preferneither_control)

mean_MSNBC_Control_ImmigrationLevel <- mean(preferMSNBC_Control$immig_increased) + mean(preferMSNBC_Control$taxes_pos) + mean(preferMSNBC_Control$jobs_pos)
mean_MSNBC_Control_ImmigrationLevel <- mean_MSNBC_Control_ImmigrationLevel / 3

mean_FOX_Control_ImmigrationLevel <- mean(preferFOX_Control$immig_increased) + mean(preferFOX_Control$taxes_pos) + mean(preferFOX_Control$jobs_pos)
mean_FOX_Control_ImmigrationLevel <- mean_FOX_Control_ImmigrationLevel / 3

mean_prefer_neither_ImmigrationLevel <- mean(preferneither_control$immig_increased) + mean(preferneither_control$taxes_pos) + mean(preferneither_control$jobs_pos)

mean_prefer_neither_ImmigrationLevel <- mean_prefer_neither_ImmigrationLevel / 3

## Confidence Interval - 

MSNBC_Control_ImmigrationLevel <- ((preferMSNBC_Control$immig_increased) + (preferMSNBC_Control$taxes_pos) + (preferMSNBC_Control$jobs_pos)) / 3

t1 <- t.test(MSNBC_Control_ImmigrationLevel)

FOX_Control_ImmigrationLevel <- ((preferFOX_Control$immig_increased) + (preferFOX_Control$taxes_pos) + (preferFOX_Control$jobs_pos)) / 3

t2 <- t.test(FOX_Control_ImmigrationLevel)

prefer_neither_immigrationlevel <- ((preferneither_control$immig_increased) + (preferneither_control$taxes_pos) + (preferneither_control$jobs_pos)) / 3

ta <- t.test(prefer_neither_immigrationlevel)

table1 <- map_df(list(t1, ta, t2), broom::tidy)
table1[c("estimate", "statistic", "p.value", "conf.low", "conf.high")]
```

Here I subset the data for those who chose their news source. This was subset for those who (1) preferred MSNBC and chose MSNBC, (2)preferred MSNBC and chose FOX, (3) preferred FOX and chose FOX, and those who (4) preferred FOX and chose MSNBC. I calculated their mean immigration support levels (higher = more liberal) based on the 3 immigration questions asked after they read the story. I also calculated their CIs in the table below.

Added those in the neither category!

# free choice - 

```{r}
# Prefer MSNBC & Chose MSNBC

preferMSNBC_Choice_Same <- subset(dat, tv_prefer > 0 & condition == "choice" & source == "MSNBC")
## View(preferMSNBC_Choice_Same)

mean_MSNBC_Choice_Same_ImmigrationLevel <- mean(preferMSNBC_Choice_Same$immig_increased) + mean(preferMSNBC_Choice_Same$taxes_pos) + mean(preferMSNBC_Choice_Same$jobs_pos)
mean_MSNBC_Choice_Same_ImmigrationLevel <- mean_MSNBC_Choice_Same_ImmigrationLevel / 3
mean_MSNBC_Choice_Same_ImmigrationLevel

## Confidence Interval

MSNBC_Choice_Same_ImmigrationLevel <- ((preferMSNBC_Choice_Same$immig_increased) + (preferMSNBC_Choice_Same$taxes_pos) + (preferMSNBC_Choice_Same$jobs_pos)) / 3

t3 <- t.test(MSNBC_Choice_Same_ImmigrationLevel)

# Prefer MSNBC & Chose Fox

preferMSNBC_Choice_Diff <- subset(dat, tv_prefer > 0 & condition == "choice" & source == "Fox News")
## View(preferMSNBC_Choice_Diff)

mean_MSNBC_Choice_Diff_ImmigrationLevel <- mean(preferMSNBC_Choice_Diff$immig_increased) + mean(preferMSNBC_Choice_Diff$taxes_pos) + mean(preferMSNBC_Choice_Diff$jobs_pos)
mean_MSNBC_Choice_Diff_ImmigrationLevel <- mean_MSNBC_Choice_Diff_ImmigrationLevel / 3
mean_MSNBC_Choice_Diff_ImmigrationLevel

## Confidence Interval

MSNBC_Choice_Diff_ImmigrationLevel <- ((preferMSNBC_Choice_Diff$immig_increased) + (preferMSNBC_Choice_Diff$taxes_pos) + (preferMSNBC_Choice_Diff$jobs_pos)) / 3

t4 <- t.test(MSNBC_Choice_Diff_ImmigrationLevel)

 # Prefer Fox & Chose Fox

preferFOX_Choice_Same <- subset(dat, tv_prefer < 0 & condition == "choice" & source == "Fox News")
## View(preferFOX_Choice_Same)

mean_FOX_Choice_Same_ImmigrationLevel <- mean(preferFOX_Choice_Same$immig_increased) + mean(preferFOX_Choice_Same$taxes_pos) + mean(preferFOX_Choice_Same$jobs_pos)
mean_FOX_Choice_Same_ImmigrationLevel <- mean_FOX_Choice_Same_ImmigrationLevel / 3
mean_FOX_Choice_Same_ImmigrationLevel

## Confidence Interval 

FOX_Choice_Same_ImmigrationLevel <- ((preferFOX_Choice_Same$immig_increased) + (preferFOX_Choice_Same$taxes_pos) + (preferFOX_Choice_Same$jobs_pos)) /  3

t5 <- t.test(FOX_Choice_Same_ImmigrationLevel)

# Prefer Fox and Chose MSNBC 

preferFOX_Choice_Diff <- subset(dat, tv_prefer < 0 & condition == "choice" & source == "MSNBC")
## View(preferFOX_Choice_Diff)

mean_FOX_Choice_Diff_ImmigrationLevel <- mean(preferFOX_Choice_Diff$immig_increased) + mean(preferFOX_Choice_Diff$taxes_pos) + mean(preferFOX_Choice_Diff$jobs_pos)
mean_FOX_Choice_Diff_ImmigrationLevel <- mean_FOX_Choice_Diff_ImmigrationLevel / 3
mean_FOX_Choice_Diff_ImmigrationLevel

## Confidence Interval

FOX_Choice_Diff_ImmigrationLevel <- ((preferFOX_Choice_Diff$immig_increased) + (preferFOX_Choice_Diff$taxes_pos) + (preferFOX_Choice_Diff$jobs_pos)) / 3

t6 <- t.test(FOX_Choice_Diff_ImmigrationLevel)

## Prefer Neither, Chose MSNBC

preferneither_Choose_MSNBC <- subset(dat, tv_prefer == 0 & condition == "choice" & source == "MSNBC")
## View(preferneither_Choose_MSNBC)

mean_preferneither_ChoseMSNBC_ImmigrationLevel <- mean(preferneither_Choose_MSNBC$immig_increased) + mean(preferneither_Choose_MSNBC$taxes_pos) + mean(preferneither_Choose_MSNBC$jobs_pos)
mean_preferneither_ChoseMSNBC_ImmigrationLevel <- mean_preferneither_ChoseMSNBC_ImmigrationLevel / 3
mean_preferneither_ChoseMSNBC_ImmigrationLevel

## Confidence Interval - 

preferneither_Choose_MSNBC_immigrationlevel <- ((preferneither_Choose_MSNBC$immig_increased) + (preferneither_Choose_MSNBC$taxes_pos) + (preferneither_Choose_MSNBC$jobs_pos)) / 3

tb <- t.test(preferneither_Choose_MSNBC_immigrationlevel)

## Prefer Neither, Chose FOX

preferneither_Choose_FOX <- subset(dat, tv_prefer == 0 & condition == "choice" & source == "Fox News")
## View(preferneither_Choose_FOX)

mean_preferneither_ChoseFOX_ImmigrationLevel <- mean(preferneither_Choose_FOX$immig_increased) + mean(preferneither_Choose_FOX$taxes_pos) + mean(preferneither_Choose_FOX$jobs_pos)
mean_preferneither_ChoseFOX_ImmigrationLevel <- mean_preferneither_ChoseFOX_ImmigrationLevel / 3
mean_preferneither_ChoseFOX_ImmigrationLevel

## Confidence Interval - 

preferneither_Choose_FOX_immigrationlevel <- ((preferneither_Choose_FOX$immig_increased) + (preferneither_Choose_FOX$taxes_pos) + (preferneither_Choose_FOX$jobs_pos)) / 3

tc <- t.test(preferneither_Choose_FOX_immigrationlevel)

table2 <- map_df(list(t3, t4, t5, t6, tb, tc), broom::tidy)
table2[c("estimate", "statistic", "p.value", "conf.low", "conf.high")]

```

## plot control vs. free choice

Control vs Free Choice - Updated plot with accurate CIs and seperate panels

```{r}
data <- data.frame(x = c("Control", "Control", "Control", "Chose MSNBC", "Chose FOX", "Chose FOX", "Chose MSNBC", "Chose MSNBC", "Chose FOX"),
                   y    = c(mean_MSNBC_Control_ImmigrationLevel, mean_FOX_Control_ImmigrationLevel, mean_prefer_neither_ImmigrationLevel, mean_MSNBC_Choice_Same_ImmigrationLevel, mean_FOX_Choice_Same_ImmigrationLevel, mean_MSNBC_Choice_Diff_ImmigrationLevel, mean_FOX_Choice_Diff_ImmigrationLevel, mean_preferneither_ChoseMSNBC_ImmigrationLevel, mean_preferneither_ChoseFOX_ImmigrationLevel),
                   CHI       = c(0.052, 0.07, 0.06, 0.047, 0.07, 0.108, 0.223, 0.059, 0.09),
                   CLO = c(0.052, 0.07, 0.06, 0.047, 0.07, 0.108, 0.223, 0.059, 0.09),
                   Preference = c("Prefer MSNBC", "Prefer FOX", "Prefer Neither", "Prefer MSNBC", "Prefer FOX", "Prefer MSNBC", "Prefer FOX", "Prefer Neither", "Prefer Neither"),
                   Group = c("Control", "Control", "Control", "Choice", "Choice", "Choice", "Choice", "Choice", "Choice"))

Choice <- ggplot(data, aes(x, y, group = Preference)) +
  geom_point() +
  geom_errorbar(aes(ymin = y + CHI, ymax = y - CLO)) +
  labs(x = "",
       y = "LIBERAL IMMIGRATION LEVEL",
       title = "FREE CHOICE") +
  theme_classic() + 
  geom_point(aes(color =Preference, shape=Group, size = Group)) + 
  scale_shape_manual(values=c(15, 17, 16)) +
  scale_size_manual(values=c(4,4,4)) +
  theme_gray(base_size = 14) + 
  theme(axis.text.x = element_text(angle = 45, size = 8, hjust = 1))+
  facet_wrap(~Preference, ncol = 3, scales = "free_x") +
  ylim(c(0:1))

Choice
```

# assigned - 

Here I subset the data for those who were assigned their news source. This was subset for those who (1) preferred MSNBC and were assigned MSNBC, (2)preferred MSNBC and were assigned FOX, (3) preferred FOX and were assigned FOX, and those who (4) preferred FOX and were assigned MSNBC. I calculated their mean immigration support levels (higher = more liberal) based on the 3 immigration questions asked after they read the story. I also calculated their CIs in the table below.

Added those in the neither category!

```{r}
## Prefer MSNBC, Assinged MSNBC

preferMSNBC_assignedMSNBC <- subset(dat, tv_prefer > 0 & condition == "assigned" & source == "MSNBC")
## View(preferMSNBC_assignedMSNBC)

mean_preferMSNBC_assignedMSNBC_ImmigrationLevel <- mean(preferMSNBC_assignedMSNBC$immig_increased) + mean(preferMSNBC_assignedMSNBC$taxes_pos) + mean(preferMSNBC_assignedMSNBC$jobs_pos)
mean_preferMSNBC_assignedMSNBC_ImmigrationLevel <- mean_preferMSNBC_assignedMSNBC_ImmigrationLevel / 3
mean_preferMSNBC_assignedMSNBC_ImmigrationLevel

## Confidence interval - 

preferMSNBC_assignedMSNBC_ImmigrationLevel <- ((preferMSNBC_assignedMSNBC$immig_increased) + (preferMSNBC_assignedMSNBC$taxes_pos) + (preferMSNBC_assignedMSNBC$jobs_pos)) / 3

t7 <- t.test(preferMSNBC_assignedMSNBC_ImmigrationLevel)

## Prefer MSNBC, Assigned FOX

preferMSNBC_assignedFOX <- subset(dat, tv_prefer > 0 & condition == "assigned" & source == "Fox News")
## View(preferMSNBC_assignedFOX)

mean_preferMSNBC_assignedFOX_ImmigrationLevel <- mean(preferMSNBC_assignedFOX$immig_increased) + mean(preferMSNBC_assignedFOX$taxes_pos) + mean(preferMSNBC_assignedFOX$jobs_pos)
mean_preferMSNBC_assignedFOX_ImmigrationLevel <- mean_preferMSNBC_assignedFOX_ImmigrationLevel / 3
mean_preferMSNBC_assignedFOX_ImmigrationLevel

## Confidence Intervals - 

preferMSNBC_assignedFOX_ImmigrationLevel <- ((preferMSNBC_assignedFOX$immig_increased) + (preferMSNBC_assignedFOX$taxes_pos) + (preferMSNBC_assignedFOX$jobs_pos)) / 3

t8 <- t.test(preferMSNBC_assignedFOX_ImmigrationLevel)

## Prefer Fox, Assigned FOX

preferFOX_assignedFOX <- subset(dat, tv_prefer < 0 & condition == "assigned" & source == "Fox News")
## View(preferFOX_assignedFOX)

mean_preferFOX_assignedFOX_ImmigrationLevel <- mean(preferFOX_assignedFOX$immig_increased) + mean(preferFOX_assignedFOX$taxes_pos) + mean(preferFOX_assignedFOX$jobs_pos)
mean_preferFOX_assignedFOX_ImmigrationLevel <- mean_preferFOX_assignedFOX_ImmigrationLevel / 3
mean_preferFOX_assignedFOX_ImmigrationLevel

## Confidence Intervals - 

preferFOX_assignedFOX_ImmigrationLevel <- ((preferFOX_assignedFOX$immig_increased) + (preferFOX_assignedFOX$taxes_pos) + (preferFOX_assignedFOX$jobs_pos)) / 3

t9 <- t.test(preferFOX_assignedFOX_ImmigrationLevel)

## Prefer FOX, Assigned MSNBC

preferFOX_assignedMSNBC <- subset(dat, tv_prefer < 0 & condition == "assigned" & source == "MSNBC")
## View(preferFOX_assignedMSNBC)

mean_preferFOX_assignedMSNBC_ImmigrationLevel <- mean(preferFOX_assignedMSNBC$immig_increased) + mean(preferFOX_assignedMSNBC$taxes_pos) + mean(preferFOX_assignedMSNBC$jobs_pos)
mean_preferFOX_assignedMSNBC_ImmigrationLevel <- mean_preferFOX_assignedMSNBC_ImmigrationLevel / 3
mean_preferFOX_assignedMSNBC_ImmigrationLevel

## Confidence Intervals - 

preferFOX_assignedMSNBC_ImmigrationLevel <- ((preferFOX_assignedMSNBC$immig_increased) + (preferFOX_assignedMSNBC$taxes_pos) + (preferFOX_assignedMSNBC$jobs_pos)) / 3

t10 <- t.test(preferFOX_assignedMSNBC_ImmigrationLevel)

## Prefer neither, Assigned MSNBC

preferneither_assignedMSNBC <- subset(dat, tv_prefer == 0 & condition == "assigned" & source == "MSNBC")
## View(preferFOX_assignedMSNBC)

mean_preferneither_assignedMSNBC_ImmigrationLevel <- mean(preferneither_assignedMSNBC$immig_increased) + mean(preferneither_assignedMSNBC$taxes_pos) + mean(preferneither_assignedMSNBC$jobs_pos)
mean_preferneither_assignedMSNBC_ImmigrationLevel <- mean_preferneither_assignedMSNBC_ImmigrationLevel / 3
mean_preferneither_assignedMSNBC_ImmigrationLevel

## Confidence Intervals - 

preferneither_assignedMSNBC_ImmigrationLevel <- ((preferneither_assignedMSNBC$immig_increased) + (preferneither_assignedMSNBC$taxes_pos) + (preferneither_assignedMSNBC$jobs_pos)) / 3

td <- t.test(preferneither_assignedMSNBC_ImmigrationLevel)

## Prefer neither, Assigned MSNBC

preferneither_assignedFOX <- subset(dat, tv_prefer == 0 & condition == "assigned" & source == "Fox News")
## View(preferFOX_assignedFOX)

mean_preferneither_assignedFOX_ImmigrationLevel <- mean(preferneither_assignedFOX$immig_increased) + mean(preferneither_assignedFOX$taxes_pos) + mean(preferneither_assignedFOX$jobs_pos)
mean_preferneither_assignedFOX_ImmigrationLevel <- mean_preferneither_assignedFOX_ImmigrationLevel / 3
mean_preferneither_assignedFOX_ImmigrationLevel

## Confidence Intervals - 

preferneither_assignedFOX_ImmigrationLevel <- ((preferneither_assignedFOX$immig_increased) + (preferneither_assignedFOX$taxes_pos) + (preferneither_assignedFOX$jobs_pos)) / 3

te <- t.test(preferneither_assignedFOX_ImmigrationLevel)

table3 <- map_df(list(t1, t2, t6, t7, t8, t9, td, te), broom::tidy)
table3[c("estimate", "statistic", "p.value", "conf.low", "conf.high")]
```

# combine and plot - 

Control vs Assigned - Updated plot with accurate CIs and seperate panels

```{r}
data2 <- data.frame(x2 = c("Control", "Control", "Control", "Assigned MSNBC", "Assigned FOX", "Assigned FOX", "Assigned MSNBC", "Assigned MSNBC", "Assigned FOX"),
                    y2    = c(mean_MSNBC_Control_ImmigrationLevel, mean_FOX_Control_ImmigrationLevel, mean_prefer_neither_ImmigrationLevel, mean_preferMSNBC_assignedMSNBC_ImmigrationLevel, mean_preferFOX_assignedFOX_ImmigrationLevel, mean_preferMSNBC_assignedFOX_ImmigrationLevel, mean_preferFOX_assignedMSNBC_ImmigrationLevel, mean_preferneither_assignedMSNBC_ImmigrationLevel, mean_preferneither_assignedFOX_ImmigrationLevel),
                    CHI_2      = c(0.052, 0.07, 0.06, 0.067, 0.084, 0.091, 0.114, 0.085, 0.066),
                    CLO_2 = c(0.052, 0.07, 0.06, 0.067, 0.084, 0.091, 0.114, 0.085, 0.066),
                    Preference2 = c("Prefer MSNBC", "Prefer FOX", "Prefer Neither", "Prefer MSNBC", "Prefer FOX", "Prefer MSNBC", "Prefer FOX", "Prefer Neither", "Prefer Neither"),
                    Group = c("Control", "Control", "Control", "Assigned", "Assigned", "Assigned", "Assigned", "Assigned", "Assigned"))

Assigned <- ggplot(data2, aes(x2, y2, group = Preference2)) +
  geom_point() +
  geom_errorbar(aes(ymin = y2 + CHI_2, ymax = y2 - CLO_2)) +
  labs(x = "",
       y = "LIBERAL IMMIGRATION LEVEL",
       title = "ASSIGNED") +
  theme_classic() + 
  geom_point(aes(color=Preference2, shape=Group, size = Group)) + 
  scale_shape_manual(values=c(15, 17, 16)) +
  scale_size_manual(values=c(4,4,4)) +
  theme_gray(base_size = 14) + 
  theme(axis.text.x = element_text(angle = 45, size = 8, hjust = 1)) +
  facet_wrap(~Preference2, ncol = 3, scales = "free_x") +
  ylim(c(0:1))

Assigned
```